Ms. No. PSRM-OA-2019-0126 entitled ``Taking Dyads Seriously''

### 2020-03-06 revisionMemo/rev1.tex
memo edits

	\item P1: ``Most standard approaches assume that the problems raised by non-iid relational data can be addressed by recalculating the standard errors of estimated parameters to reflect the potential clustering of cases. In practice, such strategies rarely work because they do not directly address the fundamental data generating process''.

@@

		We have clarified our language in the paper (on page 1) to address this question.  Strategies like those employed by Aronow et al. do not directly model all relevant dependencies in the data but instead adjust the variance estimator.\footnote{As Aronow et al. explain, “Of course, accounting for dynamic dyadic clustering may fail to fully account for all relevant dependencies in the data." p. 16.}   While such an approach decreases the risk of a type 1 error, it increases risk of type 2 error (if the mean estimate is biased downwards, increasing the variance estimate will cause us to falsely accept the null). The main aim of our research is to directly account for the relevant dependency structures in the data, thus providing an accurate estimate and addressing both types of possible errors.

@@

		\item Okay here is where the paper are starting to clarify goals.  So a) is about causal identification.  But as I understand, the solution here is parametric identification of causal effects.  This means that the issue of misspecification and robustness ought to be taken up.  Similarly, b) is addressed in this paper under a fairly simple parametric data generating process. But again, how robust is the proposed model to situations where the real DGP does not abide by the parametric assumptions (linearity, normally distributed random effects, and a factor model for the residuals of dimension K)? For c), I think most would agree that the “proof” is simply in comparison to whatever other good models are available.  Not however, that in social science applications, forecasting and therefor c) are rarely of interest (at least not in the types of research that appear in political science journals).  As such, from the perspective of what the researchers in discipline mostly cares about, a) and b) are of primary importance.

@@

For part (a), we have clarified that our study does not address causal identification. We instead focus on providing unbiased estimates of covariates, which improves inference for observational data. We have also edited P8 to read: Non-iid observations in relational data result from the fact that there is a complex structure underlying the dyadic events or processes that we observe. We have also clarified the goals of the paper in the earlier sections.}}
		\item \emph{\textcolor{blue}{As for (b), the reviewer raises an important point. How well does AME work out when the DGP does not abide by parametric assumptions we address this in the section concerning the simulation and Aronow's approach.}}
		\item \emph{\textcolor{blue}{Finally, we understand these goals are not always central to political science research, but we believe that prediction is both a valuable metric to evaluate model performance as well as a goal for scholars in and of itself, as in Gleditsch and Ward 2013; Grimmer 2015; Neunhoeffer and Sternberg 2019; Colaresi and Mahmood 2017; Mueller and Rauh 2018.}

>>>>

	\item P1: ``Most standard approaches assume that the problems raised by non-iid relational data can be addressed by recalculating the standard errors of estimated parameters to reflect the potential clustering of cases. In practice, such strategies rarely work because they do not directly address the fundamental data generating process.''

@@

		We have clarified our language in the paper (on page 1) to address this question.  Strategies like those employed by Aronow et al. do not directly model all relevant dependencies in the data but instead adjust the variance estimator.\footnote{As Aronow et al. explain, “Of course, accounting for dynamic dyadic clustering may fail to fully account for all relevant dependencies in the data." p. 16.}   While such an approach decreases the risk of a type 1 error, it increases risk of type 2 error (if the mean estimate is biased downwards, increasing the variance estimate will lead us to falsely accept the null). The main aim of our research is to directly account for the relevant dependency structures in the data, thus providing an accurate estimate and addressing both types of possible errors.

@@

		\item Okay here is where the paper are starting to clarify goals.  So a) is about causal identification.  But as I understand, the solution here is parametric identification of causal effects.  This means that the issue of misspecification and robustness ought to be taken up.  Similarly, b) is addressed in this paper under a fairly simple parametric data generating process. But again, how robust is the proposed model to situations where the real DGP does not abide by the parametric assumptions (linearity, normally distributed random effects, and a factor model for the residuals of dimension K)? For c), I think most would agree that the “proof” is simply in comparison to whatever other good models are available.  Not however, that in social science applications, forecasting and therefore c) are rarely of interest (at least not in the types of research that appear in political science journals).  As such, from the perspective of what the researchers in discipline mostly cares about, a) and b) are of primary importance.

@@

For part (a), we have clarified that our study does not address causal identification. We instead focus on providing unbiased estimates of covariates, which improve inference for observational data. We have clarified the goals of the paper in the earlier sections (such as the opening paragraph of page 1) and have also edited P8 to read: ``Non-iid observations in relational data result from the fact that there is a complex structure underlying the dyadic events or processes that we observe." }}
		\item \emph{\textcolor{blue}{As for (b), the reviewer raises an important point. How well does AME work out when the DGP does not abide by parametric assumptions? We address this in the section concerning the simulation and Aronow's approach. \textbf{SM we need to add more here}}} 
		\item \emph{\textcolor{blue}{Finally, we understand these goals are not always central to political science research, but we believe that prediction is both a valuable metric to evaluate model performance as well as a goal for scholars in and of itself, as in Gleditsch and Ward 2013; Grimmer 2015; Neunhoeffer and Sternberg 2019; Colaresi and Mahmood 2017; and Mueller and Rauh 2018 among others.}
